The Folly of Passwords

### 2014-12-13 paper.tex
Got LaTeX build to pass.

\section{The Case for a Paradigm Shift}

@@

PAM USB\parentcite{steele2005paranoid} is an additional mechanism added to
this list. It allows users of Unix systems to log in by plugging in a USB
mass storage device.

@@

The \emph{Scute} project provides a PKCS~\#11 module that allows an OpenPGP
smartcard to be used with the Network Security Services (NSS) within
the Firefox web browser (we believe Chrome also supports this, but Firefox
was used in our test network). Combined with Apache's \emph{mod_nss} (which
derives from mod_ssl), we were able to implement an authentication layer
over a web-based application that supported an OpenPGP smartcard.

NSS also allows the same key to be used within Mozilla Thunderbird for
email authentication. Alternatively, the OpenSC project provides an
OpenSSL engine for PKCS#11 implementations with which we can store an X.509
client certificate on the smartcard itself.

@@

\chapter{Conclusions and Recommendations}

>>>>

\section{The Case for a Paradigm Shift}
\label{sec:case}

@@

PAM USB\parencite{steele2005paranoid} is an additional mechanism added to
this list. It allows users of Unix systems to log in by plugging in a USB
mass storage device.

@@

The \emph{Scute} project provides a PKCS~\#11 module that allows an OpenPGP
smartcard to be used with the Network Security Services (NSS) within
the Firefox web browser (we believe Chrome also supports this, but Firefox
was used in our test network). Combined with Apache's \emph{mod\_nss} (which
derives from mod\_ssl), we were able to implement an authentication layer
over a web-based application that supported an OpenPGP smartcard.

NSS also allows the same key to be used within Mozilla Thunderbird for
email authentication. Alternatively, the OpenSC project provides an
OpenSSL engine for PKCS\#11 implementations with which we can store an X.509
client certificate on the smartcard itself.

@@

\chapter{Conclusions and Recommendations}
\label{chapter:conclusion}
